\documentclass[a4paper]{article}
\usepackage{INTERSPEECH2014,amssymb,amsmath,epsfig, epstopdf}
%\usepackage[named]{algo}
%\usepackage[numbered]{algo}
\setcounter{page}{1}
\sloppy     % better line breaks
\ninept 
%SM below a registered trademark definition
\def\reg{{\rm\ooalign{\hfil
     \raise.07ex\hbox{\scriptsize R}\hfil\crcr\mathhexbox20D}}}

%% \newcommand{\reg}{\textsuperscript{\textcircled{\textsc r}}}
\title{Confidence-Features and Confidence-Scores for ASR applications in Arbitration and DNN Speaker Adaptation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother
%\name{{\em Firstname1 Lastname1, Firstname2 Lastname2, Firstname3 Lastname3,}\\
%      {\em Firstname4 Lastname4, Firstname5 Lastname5, Firstname6 Lastname6,
%      Firstname7 Lastname7}}
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother \name{{\em Kshitiz Kumar, Ziad Al Bawab, Yong Zhao, Chaojun Liu, Yifan Gong}}

\address{Microsoft Corporation, Redmond, WA \\
{\small \tt \{kshitiz.kumar, Ziadal, yonzhao, Chaojunl, yifan.gong\}@microsoft.com}}

%
\begin{document}
\maketitle

\begin{abstract}
Speech recognition confidence-scores quantitatively represent the correctness of
decoded utterances in a [0,1] range. Confidences have primarily been used to filter out recognitions
with scores below a threshold. They have also been used in other speech applications in \emph{e.g.} Arbitration, ROVER
and high-quality data selection for model training etc. Confidence-scores are computed from a rich set of confidence-features in the speech recognition engine. While many speech applications consume confidence scores, we haven't seen adequate focus on directly consuming confidence-features in applications. In this work we build a thesis that additionally consuming confidence-features can provide big gains across confidence-related tasks. We demonstrate this for Arbitration application, where we obtain 31\% relative reduction in arbitration metric. We additionally demonstrate a novel application of confidence-scores in deep-neural-network (DNN) adaptation, where we can double the relative reduction in word-error-rate (WER) for speaker adaptation on limited data.
\end{abstract}
\noindent{\bf Index Terms}: Speech recognition, Confidence scores, Confidence predictors, Classifier, MLP

%
\section{Introduction}\label{Sec:Intro}
\input{Introduction}

\section{Background on Confidence-Features and Confidence-Scores}\label{Sec:CC-Background}
\input{BackgroundConfidence}


\section{Rich Confidence-Features for Arbitration}\label{Sec:Arbitration}
\input{ConfidenceFeatureArbitration}

\section{Confidence-Scores in DNN Speaker Adaptation Framework}\label{Sec:Adaptation}
\input{DNNAdapt}

\section{Discussion}\label{Sec:Discussion}
\input{discussion}

\section{Conclusions}\label{Sec:Conclusion}
\input{conclusion}

%\newpage
%
%\eightpt
\bibliographystyle{IEEEbib}
\bibliography{strings}
\end{document}

